Meesters TODO List

### 2023-04-01 files/Chapter2/generalvibrationmodel.tex
notes

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
\begin{eqnarray*}
	\partial^{2}_{t} w &=& \partial_{x}(\partial_{x} w - \phi), \label{eq:1D_Model:ModalPDE1}\\
	\gamma \partial^{2}_{t} \phi &=& \beta (\partial_{x} w - \phi) + \partial_{x}(\partial_{x}\phi),\label{eq:1D_Model:ModalPDE2}
\end{eqnarray*}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ with $\phi(x,t) = T(t)\tilde{\phi}(x)$.

\textcolor{red}{Commonly at this point, the method of seperation of variables is applied. This splits the partial differential equation into an eigenvalue problem and a differential equation. Instead of using this method, a formulation of the eigenvalue problem and differential equation will be assumed and we'll show that they satisfy the trial solutions.}\sout{The method of separation of variables leads to an eigenvalue problem.}

For the pinned-pinned beam, the eigenvalue problem is referred to as Problem T-1E.
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. \textcolor{red}{Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.}

Suppose the function $T$ satisfies the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0, \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray} with $\lambda$ an eigenvalue.

\textcolor{red}{Die deel copy vanaf later in die section}

\textcolor{red}{********************************************************}

It is well known that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4). A convenient reference is \cite{VV06}.

@@

**********Conclusion of the section**********

\textcolor{red}{********************************************************}

@@

\textcolor{red}{Los theorem voorlopig hier. Alles onder die theorem is soortgelyk aan wat hier bo is. Was gedoen op die variational form van Problem T1.}\\

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	\int_0^1 \lambda \tilde{w} v &=& -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v',\\
	\int_0^1 \lambda \tilde{\phi} \psi &=& -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi'.
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.\\

It is well known that the eigenvalue problem like Problem T-1EV has infinitely many solutions $\langle \tilde{w}_n \ \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. For Problem T-1 (Problem T-2 and Problem T-4 also), $\lambda_n > 0$ for all $n > 0$. A convenient reference is \cite{VV06}.\\

Corresponding to this sequence of eigenvalues, we have a sequence of solutions $(T_n(t))$:
\begin{eqnarray}
	T_n(t)=A_n\cos(\sqrt{\lambda_n}t)+B_n\sin(\sqrt{\lambda_n}t), \label{eq:1D_Model:ModalAnalysisTn}
\end{eqnarray}
(with $A_n$ and $B_n$ arbitrary constants) for the ordinary differential equation \eqref{eq:1D_Model:ModalAnalysisT}.\\

As a consequence, the system of partial differential equations of Problem T-1 has a sequence of solutions $(w_n,\phi_n)$ such that
\begin{eqnarray*}
	w_n(x,t) & = & T_n(t)\tilde{w}_n(t), \\
	\phi_n(x,t) & = & T_n(t)\tilde{\phi}_n(x).,
\end{eqnarray*} satisfying the boundary conditions. These solutions are referred to as the modal solutions and they are clearly periodic with natural angular frequencies $\sqrt{\lambda_n}$ (consequently the natural frequencies are $\frac{\sqrt{\lambda_n}}{2 \pi})$.

The formal series solution for Problem T-1 is
\begin{eqnarray*}
	\langle u \ \phi \rangle = \sum_{n=1}^{\infty} T_n(t)\langle u_n(x) \ \psi_n(x)\rangle.
\end{eqnarray*}

The article \cite{VV06} provides a rigorous method to solving the eigenvalue problem for Timoshenko beam models of different boundary conditions. This method and examples form \cite{VV06} is discussed in Chapter 4.

\subsection{General vibration problem new}
Using the pinned-pinned beam as an example, in the previous section it was shown that a formal series solution can be derived that satisfies the boundary conditions. In this section, a more general vibration problem is considered that also includes initial conditions.

>>>>

Consider the partial differential equations of a pinned-pinned Timoshenko beam (obtained by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations1D} into the equations of motion \eqref{eq:1D_Model:EquationOfMotion1D} and \eqref{eq:1D_Model:EquationOfMotion1D}):
\begin{eqnarray}
	  \partial^2_{x} w - \partial_{x}\phi &=& \partial^{2}_{t} w, \label{eq:1D_Model:ModalPDE1}\\
	  \alpha\partial_{x} w - \alpha\phi + \frac{1}{\gamma}\partial^2_{x}\phi &=&  \partial^{2}_{t} \phi,\label{eq:1D_Model:ModalPDE2}
\end{eqnarray}
with boundary conditions
\begin{eqnarray*}
	w(0,t) = 0, & &	\	 w(1,t) = 0, \label{eq:1D_Model:ModalBC1}\\
	M(0,t) = 0, & &	\	M(1,t) = 0. \label{eq:1D_Model:ModalBC2}
\end{eqnarray*}
The boundary conditions of the moments can be written in terms of $\phi$ using the constitutive equation \eqref{eq:1D_Model:ConstitutiveEquations1D}:
\begin{eqnarray*}
	\partial_{x}\phi(0,t) = 0, & & \partial_{x}\phi(1,t) = 0. \label{MA_4}
\end{eqnarray*}
Consider a trial solution $w(x,t) = T(t)\tilde{w}(x)$ and $\phi(x,t) = T(t)\tilde{\phi}(x)$. Substituting these trial solutions in \eqref{eq:1D_Model:ModalPDE1} and \eqref{eq:1D_Model:ModalPDE2} yields
\begin{eqnarray*}
	T(t)\tilde{w}''(x) - T(t)\tilde{\phi}'(x) &=& T''(t)\tilde{w}(x),\\
	  \alpha T(t)\tilde{w}'(x) - \alpha T(t)\tilde{\phi}(x) + \frac{1}{\gamma}T(t)\tilde{\phi}''(x) &=&  T''(t)\tilde{\phi}(x).
\end{eqnarray*}
Dividing by $T(t)$,
\begin{eqnarray*}
	\tilde{w}''(x) - \tilde{\phi}'(x) &=& \frac{T''(t)}{T(t)}\tilde{w}(x),\\
	  \alpha \tilde{w}'(x) - \alpha \tilde{\phi}(x) + \frac{1}{\gamma}\tilde{\phi}''(x) &=&  \frac{T''(t)}{T(t)}\tilde{\phi}(x).
\end{eqnarray*}

Therefore $\displaystyle \frac{T''(t)}{T(t)}$ must be a constant. Suppose $\displaystyle \frac{T''(t)}{T(t)} = -\lambda$. Then the function $T$ satisfies the following differential equation
\begin{eqnarray}
	\ddot{T} + \lambda T = 0. \label{eq:1D_Model:ModalAnalysisT}
\end{eqnarray}

The following problem is also obtained and is called an eigenvalue problem. \sout{For the pinned-pinned beam, this eigenvalue problem is referred to as Problem T-1E.}
\subsubsection*{Problem T-1E}\label{sssec:1D_Model:Problem:T1E}
Find $\lambda \in \mathbb{R}$ and functions $\tilde{w}$ and $\tilde{\phi}$ such that
\begin{eqnarray*}
	-\tilde{w}'' + \tilde{\phi}' &=& \lambda \tilde{w}, \label{eq:1D_Model:ProblemT1E1}\\
	-\alpha \tilde{w}' + \alpha\tilde{\phi} - \frac{1}{\gamma}\tilde{\phi}'' &=& \lambda \tilde{\phi}. \label{eq:1D_Model:ProblemT1E2}
\end{eqnarray*} with boundary conditions $\tilde{w}(0) = \tilde{w}(1) = 0$ and $\tilde{\phi}'(0) = \tilde{\phi}'(1) = 0$.

Solutions to Problem T-1E is a pair of functions $\langle \tilde{w}, \tilde{\phi} \rangle$ called the eigenfunction with corresponding eigenvalue $\lambda$. Substitution confirms that $\tilde{w} = \sin(k\pi x)$ and $\tilde{\phi} = \cos(k \pi x)$ are solutions of the differential equations and satisfy the boundary conditions.

\sout{It is well known} that the eigenvalue problem like Problem T-1E has infinitely many solutions $\langle \tilde{w}_n, \tilde{\phi}_n \rangle$ and corresponding sequence of eigenvalues $\lambda_n$. For the pinned-pinned beam (Problem T-1), $\lambda_n > 0$ for all $n > 0$ (this is also true for Problem T-2 and Problem T-4). A convenient reference is \cite{VV06}.

@@

@@

@@

\subsubsection*{Problem T-1EV}\label{sssec:1D_Model:ProblemT1EV}
Find a pair of functions $\tilde{w}$ and $\tilde{\phi}$ such that for all $t >0$, $\langle \tilde{w}\ \tilde{\phi}\rangle \in  T[0,1]$ and satisfying the equations
\begin{eqnarray*}
	 -\int_0^1 \tilde{w}'v'  + \int_0^1 \tilde{\phi} v' &=& \int_0^1 \lambda \tilde{w} v ,\\
	 -\int_0^1\alpha \tilde{w}' \psi + \int_0^1\alpha \tilde{\phi} \psi - \int_0^1\frac{1}{\gamma}\tilde{\phi}' \psi' &=& \int_0^1 \lambda \tilde{\phi} \psi .
\end{eqnarray*} for each $\langle v \ \psi\rangle \in T[0,1]$.

\subsection{General vibration problem new}
\textcolor{red}{Introduction***}

Consider Problem GVar defined in Section \ref{ssec:existence:VariationlApproach}. Assume there is no damping and no forcing.

\subsubsection*{Problem GVar}\label{sssec:existence:ProblemGVar}
Given a function $f:J\rightarrow X$, find a function $u\in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$ and for each $t\in J,\ u(t)\in V,\ u'(t) \in V,\ u''(t)\in W$ and
\begin{eqnarray}
	c(u''(t),v)+b(u(t),v) = 0 \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
\end{eqnarray}
with $u(0)=u_{0}$, $u'(0)=u_{1}$.\\

Consider a trial solution $u(t) = T(t)x$ with $x \in V$ and $x \neq 0$.

Similar to the example of the pinned-pinned beam in the previous section, substitution shows that this trial solution is a solution to \eqref{eq:existence:ProblemGVarHom} if and only if you can find a real number $\lambda$ such that 
\begin{eqnarray}
	T''  + \lambda T = 0,
\end{eqnarray}
and there exists a $x \in V$ with $x \neq 0$ such that
\begin{eqnarray}
	b(x,y) = \lambda c(x,y) \ \ \ \ \textrm{ for each } \ y \in V.
\end{eqnarray}
